---
title: "Snowy Plover Management"
author: "Jamie Miller"
date: "May 31, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## 1. Set up Leslie Matrices for snowy plover age structure population model
```{r setup matrix manually}
# Four Age Classes: Egg, Chick, Juvenile, Adult
nclasses = 4

# create a growth matrix to store fecundity and survivorship information
gmatrix=matrix(nrow=nclasses, ncol=nclasses)
gmatrix

# change NAs to zero
gmatrix[]=0.0
gmatrix

# assign values for fecundity for each of the age classes 
# notes that fecundity rates are births per capita (number in class) per time step
# At VAFB: average fledge succecss is 1.3 fledges per male; in 2019, 220 adults, 1156 eggs, 588 chicks, 134 fledges 
### 1156/220 # 5.25 eggs per adult
### 220/1156 # 0.19 adults per egg; that makes no sense as a measure of fecundity

fecund =  c(0,0,0,5.25)

# enter into our matrix
gmatrix[1,]=fecund
 
# Survivorship probabilities (to the next class) per time step, using 2019 data.
#588/1156 # 0.509 Hatch Rate, Chicks/Eggs
#134/588 # 0.228 Fledge rate, Fledges/Chicks
 
gmatrix[2,1]=0.509  
gmatrix[3,2]=0.228
gmatrix[4,3]=0.33 #Adjust this number

# Adult survivorship to the following year
gmatrix[4,4]=0.6 #Adjust this number
gmatrix

```

Now use the matrix to grow a population 
```{r test matrix}
# start with an initial population, lets say 1 individual in each class

#p0 = rep(1, times=nclasses)
p0 = c(1156,588,134,220)

# advance to the next time step
# note the use of matrix multiplication
p1 = gmatrix %*% p0
p1

# has the total number of individuals changed?
sum(p1)
sum(p0)

# growth rate
sum(p1)/sum(p0)

#add another year
p2 = gmatrix %*% p1
p3 = gmatrix %*% p2

# combined
pop = cbind.data.frame(p0,p1,p2,p3)
pop$age = c("1_Eggs","2_Chicks","3_Juveniles","4_Adults")

popl = pop %>% gather(key="timestep",value="pop",-age)
ggplot(popl, aes(timestep, pop,fill=as.factor(age)))+geom_col(position="dodge")+labs(fill="Age Group")

# I'm not sure this accomplishes what I want it to accomplish.
# Use the snpl.R function instead.

```


## 2. Use the snpl.R function to calcutlate the age structure model and predict adult population over time. 
```{r multitime}

source("../R/snpl.R")

# At VAFB: average fledge succecss is 1.3 fledges per male; in 2019, 220 adults, 1156 eggs, 588 chicks, 134 fledges 
### 1156/220 # 5.25 eggs per adult
### 220/1156 # 0.19 adults per egg; that makes no sense as a measure of fecundity

# Fecundity Rates
F_adult = 5.25*0.6 # 1156/220 # 5.25 eggs per adult, M to F ratio of 0.6 (3 males to 2 females). represents number eggs per female; adjust for diff sex ratios

# Survivorship probabilities (to the next class) per time step, using 2019 data.
#588/1156 # 0.509 Hatch Rate, Chicks/Eggs
#134/588 # 0.228 Fledge rate, Fledges/Eggs

# Survivorship - based on 2019 survivoral probabilities
p_egg = 1-50.9/100 # Hatch rate
p_chick = 1-22.8/100 # Fledge rate
p_fledge = 1-33/100 # First Winter Survival, assume 33% make it; Adjust this value as needed.
p_adult = 1-66/100 # Adult survivorship, assume 66% make it; Adjust this value as needed.


# initial population parameters
# In 2019, 1156 eggs, 588 chicks, 134 fledges, 220 adults
ini = c(1156,588,134,220)
n_years = 15
fert_snpl = c(0,0,0,F_adult)
surv_snpl = c(p_egg,p_chick,p_fledge,p_adult)
K = 10000 # VAFB Carrying capacity, based on Recover Goals; lookup actual value and adjust 
   ### K is not working in the model the way I thin kit should. Want it to apply only to adults, but it is applying to all life stages.
   ### Consider removing K from model and representing this information graphically.
### ===================================================================================
### changed code in snpl.R(line 41~44), and now K only applies to adult population. ###
### ===================================================================================

snpl_pop=snpl_popK(fert_snpl, surv_snpl, ini, n_years,K) # Population Structure

head(snpl_pop)

# Plot adult population by year
year = seq(from=1, to=n_years)
snpl_tot = cbind.data.frame(year=year, adult_pop=snpl_pop$pop_structure[4,])

ggplot(snpl_tot, aes(year, adult_pop)) +
         geom_col() +
         labs(y="Total Adult SNPL Population")


# Plot all ages by year
snpl_ages = cbind.data.frame(year=year, t(snpl_pop$pop_structure))
snpl_agesl = snpl_ages %>% 
  gather(key="agecat", value="pop",-year)

ggplot(snpl_agesl, aes(year, pop, fill=agecat)) +
  geom_col() +
  labs(y="Population", fill="Age Group")

# The following graphs predict snowy plover adult population and age structure over 15 years if 2019 fecundity and survivorship rates apply to all years.

```

<<<<<<< HEAD
## Next step: Apply Habitat and Predator Management Functions
```{r}

# Output matrix of predator MGMT should go into snpl.R

source("../R/predator_mgmt.R")
source("../R/snpl.R")
library(tidyverse)

funding = 6 #in thousands?
raven_p = raven_pop(n_years, 83, 0.4, 100, mgmt_action = T, funding, rmv_eff= 9, min = 0.4)
falcon_p = falcon_pop(n_years, 47, 0.3, 60, mgmt_action = T, funding, rmv_eff= 4, min = 0.6)

print(raven_p)
print(falcon_p)

tmp = list(egg_predation(raven_p), chick_predation(raven_p, falcon_p), juvenile_predation(falcon_p), adult_predation(falcon_p))
x = list(raven_p, falcon_p)


predatorpop_matrix = x %>% unlist() %>% matrix(ncol=n_years, byrow = T)
# row1= raven, row2=falcon

predation_matrix = tmp %>% unlist() %>% matrix(ncol=n_years, byrow = T) #%>% as.data.frame()
# row1= egg, row2= chick, row3=juvenile, row4=adult

rm(tmp,x)

snpl_pop2=snpl_pop2(fert_snpl, surv_snpl, ini, n_years, K, predation_matrix) # Test purpose
snpl_tot2 = cbind.data.frame(year=year, adult_pop=snpl_pop2$pop_structure[4,])

snpl_pop3=snpl_pop3(fert_snpl, surv_snpl, ini, n_years, K, predatorpop_matrix) # Test purpose
snpl_tot3 = cbind.data.frame(year=year, adult_pop=snpl_pop3$pop_structure[4,])


{
  p1<-ggplot(snpl_tot2, aes(year, adult_pop)) +
         geom_col() +
         labs(y="Total Adult SNPL Population")

  # Plot all ages by year
  snpl_ages2 = cbind.data.frame(year=year, t(snpl_pop2$pop_structure))
  snpl_agesl2 = snpl_ages2 %>% 
  gather(key="agecat", value="pop",-year)

  p2<-ggplot(snpl_agesl2, aes(year, pop, fill=agecat)) +
  geom_col() +
  labs(y="Population", fill="Age Group")
  
  show(p1)
  show(p2)
}



### Something wrong...
{
  p1<-ggplot(snpl_tot3, aes(year, adult_pop)) +
=======
## 3. Apply Habitat and Predator Management Functions
```{r multitime}

source("../R/snpl.R")
source("../R/habit.R")
source("../R/predator_mgmt.R")

# At VAFB: average fledge succecss is 1.3 fledges per male; in 2019, 220 adults, 1156 eggs, 588 chicks, 134 fledges 
### 1156/220 # 5.25 eggs per adult
### 220/1156 # 0.19 adults per egg; that makes no sense as a measure of fecundity

# Fecundity Rates
F_adult = 5.25*0.6 # 1156/220 # 5.25 eggs per adult, M to F ratio of 0.6 (3 males to 2 females). represents number eggs per female; adjust for diff sex ratios

x

# Survivorship probabilities (to the next class) per time step, using 2019 data.
#588/1156 # 0.509 Hatch Rate, Chicks/Eggs
#134/588 # 0.228 Fledge rate, Fledges/Eggs

# Survivorship - based on 2019 survivoral probabilities
p_egg = 1-50.9/100 # Hatch rate
p_chick = 1-22.8/100 # Fledge rate
p_fledge = 1-33/100 # First Winter Survival, assume 33% make it; Adjust this value as needed.
p_adult = 1-66/100 # Adult survivorship, assume 66% make it; Adjust this value as needed.


# initial population parameters
# In 2019, 1156 eggs, 588 chicks, 134 fledges, 220 adults
ini = c(1156,588,134,220)
n_years = 15
fert_snpl = c(0,0,0,F_adult)
surv_snpl = c(p_egg,p_chick,p_fledge,p_adult)
K = 10000 # VAFB Carrying capacity, based on Recover Goals; lookup actual value and adjust 
   ### K is not working in the model the way I thin kit should. Want it to apply only to adults, but it is applying to all life stages.
   ### Consider removing K from model and representing this information graphically.

snpl_pop=snpl_popK(fert_snpl, surv_snpl, ini, n_years,K) # Population Structure

head(snpl_pop)

# Plot adult population by year
year = seq(from=1, to=n_years)
snpl_tot = cbind.data.frame(year=year, adult_pop=snpl_pop$pop_structure[4,])

ggplot(snpl_tot, aes(year, adult_pop)) +
>>>>>>> d6dc584ca354411254312338eab24bdf185139e3
         geom_col() +
         labs(y="Total Adult SNPL Population")


# Plot all ages by year
<<<<<<< HEAD
  snpl_ages3 = cbind.data.frame(year=year, t(snpl_pop3$pop_structure))
  snpl_agesl3 = snpl_ages3 %>% 
  gather(key="agecat", value="pop",-year)

  p2<-ggplot(snpl_agesl3, aes(year, pop, fill=agecat)) +
  geom_col() +
  labs(y="Population", fill="Age Group")
  
  show(p1)
  show(p2)
}
=======
snpl_ages = cbind.data.frame(year=year, t(snpl_pop$pop_structure))
snpl_agesl = snpl_ages %>% 
  gather(key="agecat", value="pop",-year)

ggplot(snpl_agesl, aes(year, pop, fill=agecat)) +
  geom_col() +
  labs(y="Population", fill="Age Group")

# The following graphs predict snowy plover adult population and age structure over 15 years if 2019 fecundity and survivorship rates apply to all years.
>>>>>>> d6dc584ca354411254312338eab24bdf185139e3

```







### snp





